---
title: "Fix the title"
author: "Your Name Here"
date: "Add the date"
output: 
    html_notebook
---

### Question 1: Subsetting

#### Select the element in 10th row and 5th column in `iris` dataset

```{r}
data(iris)
iris[10, 5]
```


#### Select the Species column in `iris` dataset and print the last 5 rows of that column
```{r}
tail(iris[,"Species"], 5)
```


#### What is the average Sepal Length of flowers with Petal widths greater than 1? 

```{r}
aboveOne <- iris |> 
  subset(Petal.Width > 1)

mean(aboveOne$Sepal.Length)
```

### Question 2: For Loops

#### Write a `for` loop that iterates over the numbers 1 to 10. If the number less than 5 print the multiple of 3 (multiply the number by 3), and if the number is greater than or equal to 5 print the multiple of 2 (multiply the number by 2). 

```{r}
for(i in 1:10) {
  print(if(i < 5) {
    i * 3
  } else {
    i * 2
  })
}
```

### Question 3: While loops

#### Write a `while` loop that prints out random normal numbers with mean equal 1 and standard deviation 2 (use rnorm()) but stops (breaks) if you get a number bigger than 3. Do not change the value inside set.seeed.
```{r}
set.seed(184)

random_number = 0

while (random_number < 3) {
  random_number = rnorm(1, mean = 1, sd = 2)
  print(random_number)
}
```

### Question 4: for loops in data tables

#### Use a nested for loop that produces the following data frame. Name the dataframe  `Counting` and the variables (columns)  V1, V2, V3, and V4.  (There are 3 loops). 

Hint: First identify the pattern(s) in the table before you create the for loop.

| V1 | V2 | V3 | V4 |  
|:-- |:-- |:-- |:-- |
| 1 | 2 | 3 | 4 |  
| 2 | 3 | 4 | 5 |  
| 3 | 4 | 5 | 6 |  

```{r}
Counting <- data.frame(
  V1 = integer(),
  V2 = integer(),
  V3 = integer(),
  V4 = integer()
)

for(i in 1:3) {
  Counting <- rbind(
    Counting, 
    data.frame(
      V1 = i,
      V2 = i + 1,
      V3 = i + 2,
      V4 = i + 3
    )
  )
}

Counting

```

I couldn't figure out how to use a nested loop to create the table without creating a bunch of extra values, so I'm at the least including code that produces the desired table.

### Question 5: user defined functions

#### 5A) Complete the following user define function to generate `n` random normal numbers with a given mean and standard deviation and plot a histogram of it. Do not change  the seed number in set.seed. You can use the function `hist` to plot the histogram.  

##### 5B) Then call the function to generate 1000 random normal numbers with mean 0 and standard deviation 1 and plot a histogram of it.

```{r}
set.seed(184)
plotNormal <- function(repetitions, mean, sd){
  nums <- rnorm(repetitions, mean = mean, sd = sd)
  hist(nums)
}

plotNormal(1000, 0, 1)
```

##### Extra Credit: 

Repeat parts 5A and 5B, and add 

1. A title that say "Histogram from a Normal(`mean`, `sd`) Distribution", but the user given values of `mean` and `sd`.
2. an argument to change the color of the histogram.  

Call the function to generate 1000 random normal numbers with mean 0 and standard deviation 1 and plot a histogram. Make the bins blue.

```{r}

set.seed(184)
plotNormal <- function(repetitions, mean, sd, histColor){
  nums <- rnorm(repetitions, mean = mean, sd = sd)
  hist(nums,
       main = sprintf("Histogram from a Normal(%d, %d) Distribution", mean, sd),
       col = histColor
       )
}

plotNormal(1000, 0, 1, "blue")

```
